A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-10-04 paper/paper.tex
paper: hottbook bib

\subsection{Homotopy type theory}
Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}. HoTT is based on the notion of a basic \textsf{Type}, and the notion of sets can be recovered as \textsf{HSet}, where \texttt{HSet} is a straightforward packaging of two fields:

@@

In the \texttt{HSet} universe, three properties hold:

@@

In HoTT, the latter correspondence can be expressed, for $T: \textsf{Type}$, as an equivalence between $\Sigma S: \textsf{Type}\;.\;S \rightarrow T$ and $T \rightarrow \textsf{Type}$, which can be proved using univalence. This correspondence also holds on \textsf{HSet}, for $T: \textsf{HSet}$:

>>>>

\subsection{Homotopy type theory}
Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}. HoTT is based on the notion of a basic \textsf{Type}, and the notion of sets can be recovered as \textsf{HSet}, where \textsf{HSet} is a straightforward packaging of two fields:

@@

In the \textsf{HSet} universe, three properties hold:

@@

The latter correspondence can be expressed in HoTT, for $T: \textsf{Type}$, as an equivalence between $\Sigma S: \textsf{Type}\;.\;S \rightarrow T$ and $T \rightarrow \textsf{Type}$, which can be proved using univalence. This correspondence also holds on \textsf{HSet}, for $T: \textsf{HSet}$:
